---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# equi7grid

<!-- badges: start -->
[![R-CMD-check](https://github.com/mdsumner/equi7grid/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/mdsumner/equi7grid/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of equi7grid is ... currently a barebones get equi7 and plot it. 

The [Equi7Grid](https://github.com/TUW-GEO/Equi7Grid) is a project here: https://github.com/TUW-GEO/Equi7Grid

It aims to define 7 global zones that are better than the current UTM and MGRS grid for classifying high resolution satellite imagery. 


## Example

This plots each zone with its local centre in native Azimuthal Equidistant projection, the orange point shows the poles when they are in the frame. 


Note that we have a single vector source Geopackage, with the 7 zones in it, each in their own native projection. 

```{r example}
library(equi7grid)
dsn <- "/vsicurl/https://github.com/mdsumner/equi7grid/raw/main/data-raw/equi7grid.gpkg"


m <- do.call(cbind, maps::map(plot = F)[1:2])
library(terra)
layers <- vector_layers(dsn)
par(mfrow = n2mfrow(length(layers)), mar = rep(0, 4))
for (i in seq_along(layers)) {
  v <- vect(dsn, layers[i])
  ex <- as.vector(ext(v))
  m1 <- project(m, to = crs(v), from = "EPSG:4326")
  m1 <- m1[m1[,1] >= ex[1] & m1[,1] <= ex[2] & m1[,2] >= ex[3] & m1[,2] <= ex[4], ]
  plot(NA, axes = FALSE, xlim = ex[1:2], ylim = ex[3:4], asp = 1, xlab = "", ylab = "")
  plot(v, axes = F, border = "firebrick", add = TRUE)
  lines(m1, col = rgb(0, 0, 0, .5))
  pt <- cbind(0, c(-90, 90))
  p0 <- project(pt, to = crs(v), from = "EPSG:4326")
points(p0, pch = "+", cex = 2, col = "orange")
box(col = "lightgrey")

}





```

In the package we can read the entire set from a single FlatGeobuf, but you'll need to use them locally as they don't make sense in one single CRS. 

The crs is recorded on each, but obviously we can craft our own scene and projection, here we just focus on the south in LAEA.

```{r fgb}
library(equi7grid)
fgb <- system.file("extdata/equi7_longlat.fgb", package = "equi7grid", mustWork = TRUE)
library(terra)
x <- vect(fgb)
m <- do.call(cbind, maps::map(plot = F)[1:2])
crs <- "+proj=laea +lat_0=-90"
plot(project(x[-(3:5), ], crs), col = hcl.colors(4))
lines(project(m, to = crs, from = "EPSG:4326"))
```


## Code of Conduct
  
Please note that the equi7grid project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
